\chapter{Appendix}

\section{Concept Matrix}
The Concept Matrix \ref{tab:concept_matrix} maps each paper to concepts of neural networks they support. These concepts are \ac{CNN}s (Conv.), residual networks (Res.), inception networks (Inc.), capsule networks (Caps.), dense convolutional neural networks (Dense), and depthwise separable convolutional neural networks (Sep. Conv.).
\input{img/conceptmatrix}

\section{Benchmark Datasets}
Performance of neural networks for image classification is measured on benchmark datasets. The benchmark datasets are listed below. 
\label{sec:benchmark}
\input{append/benchmark}

\section{Inclusion and Exclusion Criteria}
The inclusion and exclusion criteria determine whether or not a paper is selected for the literature review. The inclusion and exclusion criteria are listed below.
\label{sec:krit}
\input{append/criteria}

\section{Literature Source List}
The literature source list lists all sources of papers. These sources are journals, conference proceedings, full-text databases, image classification leaderboards, and scientific search engines. The literature source list is displayed below.
\label{sec:source}
\input{append/litsource}

\section{Term Table}
The term table lists terms related to the problem statement described in Section \ref{sec:problem}. As a result, the term table contains all terms that can be used to derive search queries. The term table is displayed below.
\label{sec:termtable}
\input{img/termtable}

%\section{Dataset Term Table}
%\label{sec:datasettermatable}
%\input{img/datasettermtable}

\section{Contents of the Digital Appendix}
\label{sec:digiappend}
The dataset and code used to conduct the experiment are appended in the digital appendix. The digital appendix is provided on the enclosed USB flash drive $D$. The contents of the digital appendix are listed in Table \ref{tab:digiappend}.
\input{img/digiappend}