\chapter{Methodology}
\label{chp:metho}
This paper seeks to determine the best-performing neural network for tool image classification. In the course of the literature review conducted by this paper, no paper about neural networks for tool image classification was found. On that account, the neural network is determined based on the state of the art of neural networks for image classification.
This chapter defines the methodology to determine this neural network. To determine this neural network the state-of-the-art neural networks need to be compared in regard to their performance.
Therefore, a metric, a dataset, and the state-of-the-art neural networks are required.
The metric operationalizes performance. Thus, performance is comparable. The metric is selected and defined in Section \ref{sec:metric}.
The dataset is required to train and evaluate the neural networks. \autocite{LeCun.2015} The methodology of the dataset construction is defined in Section \ref{sec:datasetconstruction}.
This paper focuses on the state of the art of neural networks for image classification, see Section \ref{sec:scope}. The state of the art is analyzed in the course of a literature review conducted by this paper. The methodology of the literature review is defined in Section \ref{sec:litrev}.
The best-performing neural network for tool image classification is determined in the course of an experiment. This experiment is described in Section \ref{sec:experiment}.

\section{Metric}
\label{sec:metric}
\input{metho/metric}

\section{Dataset Construction}
\label{sec:datasetconstruction}
\input{metho/dataset}

\section{Literature Review}
\label{sec:litrev}
\input{metho/litrev}

\section{Experiment}
\label{sec:experiment}
\input{metho/experiment}