% Lit Rev => SOTA Models
% Experiment => POC, SOTA Models und Ref Impl. for own implementation
For industry aiming to implement augmented reality solutions for field workers, the results of the literature review conducted by this paper and the implementation of the neural networks may be of special interest. Implementing augmented reality solutions for field workers requires software perceiving the environment of field workers. The environment can be perceived through computer vision. The results of the literature review conducted by this paper comprise common concepts of neural networks and state-of-the-art neural networks for image classification. These concepts are shared across a variety of neural networks for different computer vision tasks, for example, semantic segmentation, object detection, image generation, pose estimation, and facial recognition \autocites{Yuan.2019}{Tan.2019b}{Karras.2018}{Bulat.2020}{Yan.2019}. The state-of-the-art neural networks for image classification implement these concepts. To conduct the experiment, these neural networks are implemented. The implementations are appended in the digital appendix, see Section \ref{sec:digiappend}. As a result, these concepts and implementations can be used as a basis for implementing software perceiving the environment of field workers and, thus, as a basis for implementing augmented reality solutions for field workers. Furthermore, this paper can be seen as proof of concept for software perceiving the environment of field workers.